---
title: "WUP_04"
author: "Nadya Mitwasi"
date: "Spring 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We will load in the data and there is multipul levels degrees. there fore we will use anova.  

# Results
```{r}
worlddata=read.csv(file="GSScsv.csv",header=T)
```
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
model1 <- aov(WORDSUM~DEGREE,data=worlddata)
summary.aov(model1)
```

The P value is 0.000236 which is less than 0.05 that means we have evidence that there a significant difference in the means at least one of the combinations but we dont know which one.  
we used TUKEY-HSD test to see where the differences are.  

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 12.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```
The only significant difference is in wordsum between the High school graduate and the LT high school graduate.  

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We used anovs to work out the P value and we got it it turns out that the P value is 0.000236 which is less than 0.05 This means that at least one of the differences is shown to be considerably different in the mean, but we don't know which one.  
We used the TUKEY-HSD test to see where the deviations are. It reveals that the only major difference between high school graduates and secondary school graduates is in vocabulary. We've got a confident 95% chart rating and it's seen.  
